---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753noah)
```

# Intro 

This is my final package for MATH4751. In this file will explain the use of scatterhist, ntickets, mycltb, and myboot. Addionally this file will explain and analyze fire.rda.

## scatterhist

scatterhist takes two vectors, x and y, and creates a scatterplot of the points with histograms of the vectors.
```{r}
# set seed for consistent results
set.seed(40)
# getting random data to plot
x = rnorm(10, 10, 5)
y = rnorm(10, 5, 8)
# plotting the random data
MATH4753noah::scatterhist(x, y, "X", "Y")
```

## ntickets

ntickets gives the solution to the "overbooking problem". Given a number of seats to sell tickets for, the desired probability of overbooking occurring, and the probability of a ticket holder to take a seat, it will output two graphs for the discrete and continuous cases and will list the solutions.
```{r}
MATH4753noah::ntickets(400, .04, .95)
```

## mycltb

mtcltb returns a graph of a histogram of the mean value of binomial distributions. The parameters are the sample size of the binomial, the probability of success of the binomial, and the number of distributions created.
```{r}
MATH4753noah::mycltb(10, 10000, p=0.25)
```

## myboot

myboot2 bootstraps a given sample to create a confidence interval for a given statistic. It will output a graph of the results of the bootstrapping along with the interval. 
This function will be used to analyze the fire data. fire holds the distance traveled and damage done by fires. Using this data as a sample, myboot will find a confidence interval of the mean damage for the population of all fires.
```{r}
fires_damage = MATH4753noah::fire$DAMAGE
head(fires_damage)
ci = myboot2(iter = 10000, x = fires_damage, alpha = 0.05)
ci$ci
```
